Evaluation of Machine Translation Pre-Trained Models for Many-to-English Translation

### 2024-08-22 paper/paper.tex
updated

Since the introduction of Transformers in 2017 \cite{vaswani-2017-attention}, Natural Language Processing (NLP) and machine translation in particular reached a giant milestone. The following years saw the birth of Large Language Models (LLMs) such as BERT \cite{devlin-2019-bert}, GPT \cite{openai-2024-gpt4}, and T5 \cite{raffel-2023-t5}, which revolutionised both MT and the whole field of NLP. Then in the early 2020s, several pre-trained models that are specifically designed for machine translation emerged, these will be referred in this paper as Machine Translation Pre-Trained Models (MT-PTMs). OPUS-MT \cite{tiedemann-2020-opus-mt} produced numerous models designed for one-to-one translations. Additionally, multilingual models: mBART-50 \cite{liu-2020-mbart}, NLLB-200 \cite{nllb200-2020}, and M2M-100 \cite{fan-2020-m2m100} have also been published, growing popularity as multilingualism has been shown to allow for sharing information among languages \cite{garcia-2020-multilingual}. Most of these models are trained on a diverse set of languages, allowing for many-to-many translation, which is able to translate between any of the supported pairs of languages. This allows the models to generalise over shared lexical and linguistic among languages, and have been shown to increase performance compared to one-to-one translation models \cite{liu-2020-mbart}.

@@

Nevertheless, there does not seem to be much work on comparing or benchmarking different MT-PTMs in machine translation. Intento recently published 'The State of Machine Translation 2024' \cite{intento-2024} providing an in-depth evaluation of 52 MT engines and LLMs across 11 language pairs. Figure \ref{fig:intento_quality} shows the reported translation quality across different domains and language pairs, showing that the results significantly varies based on these parameters. They also reported a lack of growth in the number of supported languages and concluded that translation quality significantly varies depending on languages \cite{intento-2024}. However, the biggest drawback in this report is that the selected LLMs are general LLMs such as GPT-4 \cite{openai-2024-gpt4}, LLaMa2 \cite{touvron-2023-llama2}, and Mistral \cite{jiang-2023-mistral-7b}, instead of MT-specific models.

@@

Corpora are large and structured sets of texts used for linguistic research and analysis. Thus, parallel corpora are defined as sets of texts in a given source language along with their translations in another target language \cite{lefer-2020-parallel-corpora}. It can be bilingual or multilingual and is crucial for training and evaluating machine translation. Languages without or with limited parallel corpora are referred to as low-resource languages.

Since the early 2000s, English has often been used as an intermediary language, meaning texts originally written in languages are first translated into English, and then from English into other languages, resulting in most target texts being translations of translations \cite{lefer-2020-parallel-corpora}. This is called indirect translation and poses many problems in translations as terms can be ambiguous with varying or similar meanings \cite{rosa-2017-indirect-translation-problems}.

Neural Machine Translation (NMT) systems require vast amounts of training data, and thus the availability of parallel corpora is crucial for building effective models \cite{koehn-2017-challenges}. The lack of extensive parallel corpora, especially for low-resource languages, leads to suboptimal performance in NMT techniques compared to their high-resource counterparts \cite{ranathunga-2023-nmt-low-res}. OPUS \cite{opus} is a comprehensive collection of open-source parallel corpora used extensively in the field of machine translation (MT). It includes corpora for 744 languages and contains over 1,210 different datasets, amassing a total of 45,945,946,108 sentence pairs. Tatoeba \cite{tatoeba} is another prominent resource in the field of MT and NLP, known for its extensive collection of translated sentences. As of July 2024, it contains 12,186,207 sentences over 423 supported languages, growing daily through volunteer contributions. There are currently
86,915 members contributed through the Tatoeba website.

Several datasets are often used for evaluation in machine translation. The Tatoeba Challenge \cite{tiedemann-2020-tatoeba-challenge} covers 487 languages in 4,024 language pairs, including 657 test sets sourced from the Tatoeba website, covering 138 languages. The TED Talks dataset \cite{ye-2018-word-embeddings-ted} contains transcripts from TED talks for more than 50 languages. IWSLT \cite{agarwal-iwstl-2023} also contains TED talks data, but paired with English translations. Finally, WMT (Conference on Machine Translation) \cite{barrault-2020-wmt}, previously named Workshop on Statistical Machine Translation, is an annual event that organises tasks for machine translation and provides a collection of datasets for benchmarking and evaluating translation systems.

While these datasets can be used to evaluate translation performance between any language pairs, they do not contain parallel corpora between multiple different languages. A corpus between English and French, for example, contains different sets of text than a corpus between English and Spanish. Therefore, they do not support easy evaluation for many-to-English translations. Furthermore, papers often use different datasets and versions to evaluate their model performance, making direct comparisons challenging. mBART \cite{liu-2020-mbart} uses WMT19 for English-German translation and TED15 for Chinese-English translation. M2M-100 \cite{fan-2020-m2m100} uses seven different datasets shared across languages. NLLB-200  \cite{nllb200-2020} uses the FLORES dataset, designed for low-resources languages. OPUS-MT \cite{tiedemann-2023-democratizing,tiedemann-2020-opus-mt} models are evaluated using the datasets from Tatoeba challenges.

@@

% The original paper is 192 pages long and impossible to be dissected in just one section.

@@

Bilingual Evaluation Understudy (BLEU) \cite{papieni-2002-bleu} is the most commonly used metric for machine translation (MT). It assesses how well a candidate translation matches the reference translation using precision metrics for n-grams and incorporates a brevity penalty to prevent overly short translations from achieving high scores.

@@

The machine translation community relies heavily upon the BLEU score, despite its several drawbacks. The metric has been reported to not correlate strongly with human judgement, showing variations in translation that could mean that a higher BLEU score does not necessarily indicate a true enhancement in translation quality \cite{callison-burch-2006-reevaluating-bleu}. Furthermore, the metric is tokenisation-dependant, making it challenging to directly compare BLEU scores between paper \cite{post-2018-sacrebleu}. Thus, the author proposed a standardised variant called SacreBLEU \cite{post-2018-sacrebleu}, which is essentially a Python script that applies its own metric-internal preprocessing and produces the same values as WMT \cite{barrault-2020-wmt}, utilising the WMT (2008–2018) and IWSLT 2017 \cite{cettolo-etal-2017-iwslt} test sets.

@@

Metric for Evaluation of Translation with Explicit ORdering (METEOR) \cite{lavie-2007-meteor} assesses a translation by calculating a score that reflects explicit word-to-word matches between the reference and a candidate translation \cite{agarwal-2008-meteor-mbleu-mter}. It is designed to address some limitations of the BLEU score, allowing matches between simple morphological variants and synonyms. The formula is defined as:
\begin{equation}
    \text{METEOR} = (1 - \gamma \cdot \text{frag}) \cdot \frac{P \cdot R}{\alpha \cdot P + (1 - \alpha) \cdot R}
\end{equation}
where \(P\) is the precision, \(R\) is the recall, and \(\text{frag}\) is the fragmentation penalty. \(\gamma\) is a parameter that controls the weight of the fragmentation penalty, commonly set to 0.5, and \(\alpha\) is a parameter that controls the balance between precision and recall, commonly set to 0.9,

@@

OPUS-MT models are taken from the Helsinki-NLP repository through the Hugging Face website \cite{huggingface,zhang-2023-fine-tuning} with the exception of Hebrew-to-English models taken directly from 'tiedeman/opus-mt-he-en'. The 'mbart-large-50-many-to-many-mmt', the 'm2m100\_418M', and the 'nllb-200-distilled-600M' model variants are used for mBART-50 \cite{liu-2020-mbart}, M2M-100 \cite{fan-2020-m2m100}, and NLLB-200 \cite{nllb200-2020}, respectively. Similarly, all multilingual models are downloaded using the transformers \cite{wolf-2020-transformers} library from Hugging Face \cite{huggingface}. A batch size of 4 is used in all models. Translations from each source language to english are first generated through inference and saved into CSV files, before calculating the metrics score.

@@

Table \ref{table:opus_result}, \ref{table:mbart_result}, \ref{table:m2m_result}, and \ref{table:nllb_result}, and  shows the result from all four PTMs. All models perform similarly low on BLEU score across all languages, with NLLB-200 reaching 0.01 below on Japanese translation. The BLEU scores are very low (below 10 BLEU) in all cases due to the sentences being short (find cite). This also highlights the superiority of SacreBLEU compared to the flawed, standard BLEU.

% BLEU is notoriously unreliable for very short texts. The score will be disproportionately influenced by small differences if there isn't much text to begin with because there is a Brevity Penalty set in place to discourage the model from outputting fewer words and getting a high score.

@@

The BLEU, SacreBLEU, and METEOR scores gained by each model, categorised by every language pairs are illustrated in Figure \ref{fig:result_visual}. Dutch, Italian, and Ukrainian translations generally score higher across all metrics, suggesting that these languages are well-supported by the pre-trained models. Japanese translations, however, pose significant challenges for all models, as indicated by the consistently low scores across all metrics. Japanese-to-English translation seems to have the worst score on average across the four models, but particularly bad on multilingual models. In contrast, Dutch and German have consistently high results on all models except for NLLB-200, often reaching close to the highest language SacreBLEU and METEOR scores.

@@

Visualisations of the average SacreBLEU and METEOR, categorised by model (left figures) and language (right figures) is shown in Figure \ref{fig:average_bars}, providing a closer insight on how each model and language perform independently. It can be seen that when averaged across all languages, mBART-50 performs more closely to OPUS-MT on the METEOR score than the SacreBLEU score. Language-wise, Italian, Polish, and Turkish achieve the best average SacreBLEU scores while Chinese, Polish, and Turkish are the top three languages with the highest average METEOR scores.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.8\linewidth]{figures/opus_bleu_comparison.png}
    \caption{Comparison between reported OPUS-MT models performance and performance in this experiment.}
    \label{fig:opus_comparison}
\end{figure}

@@

While this study's experiments resulted in a moderately higher overall SacreBLEU, the dataset used here is also significantly smaller than the full Tatoeba challenge dataset \cite{tiedemann-2020-tatoeba-challenge} that are used in the OPUS-MT reported BLEU. In contrast, this study employs the same set of parallel sentences for all languages, which should lead to more consistent results. Nevertheless, a direct comparison between these results is not fully pertinent.

@@

Additionally, Table \ref{table:opus_comparison} shows the full scores of both results SacreBLEU and reported BLEU from each OPUS-MT model \cite{tiedemann-2020-opus-mt}. The reported BLEU scores are taken from each model card in the HuggingFace repository \cite{huggingface}. Unfortunately, other models are not benchmarked on the Tatoeba dataset, not evaluated on the source languages used in this study, and use different metrics \cite{liu-2020-mbart,fan-2020-m2m100,nllb200-2020}, and therefore cannot be directly compared to the results of this study.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.9\linewidth]{figures/inference_timings.png}
    \caption{Inference timings for every model.}
    \label{fig:inference_timings}
\end{figure}

@@

This study's findings show that while multilingual models have been shown to achieve higher performance compared to one-to-one translation models \cite{liu-2020-mbart}, this does not hold on short sentences, many-to-English translations across the 14 source languages, with regard to unfine-tuned multilingual models in this study.

OPUS-MT achieves the best performance across all 14 languages. mBART-50 is the second-best-performing model, beating OPUS-MT only in Polish SacreBLEU. Nevertheless, both the mBART-50 and the M2M-100 models perform generally well in all languages. NLLB-200, however, achieves much lower scores in both SacreBLEU and METEOR for all languages except for Chinese, slightly outperforming M2M-100 but still slightly below mBART-50. NLLB-200 should then be avoided for use without any further fine-tuning on these languages. Note that that the distilled version is used in this study for NLLB-200 instead of the larger 3.3 billion parameters model variant.

@@

When the dataset is curated, only the first translation of the same English phrases is taken, the others are discarded. This ignores several possible translation references which may include synonyms or different phrasings, thus affecting the evaluation score, especially for BLEU and SacreBLEU metrics.

The dataset consists of mostly short sentences, with little or none linguistic depth. Whether the result of this study stays consistent for longer sentences or documents is not known and should be further looked into. The Tatoeba dataset \cite{tiedemann-2020-tatoeba-challenge} consisting of short sentences has been reported to be too optimistic when evaluated with other datasets that are more realistic \cite{tiedemann-2020-opus-mt}.

>>>>

Since the introduction of Transformers in 2017 \cite{vaswani-2017-attention}, Natural Language Processing (NLP) and machine translation in particular reached a giant milestone. The following years saw the birth of Large Language Models (LLMs) such as BERT \cite{devlin-2019-bert}, GPT \cite{openai-2024-gpt4}, and T5 \cite{raffel-2023-t5}, which revolutionised both MT and the whole field of NLP. Then in the early 2020s, several pre-trained models that are specifically designed for machine translation emerged, these will be referred to in this paper as Machine Translation Pre-Trained Models (MT-PTMs). OPUS-MT \cite{tiedemann-2020-opus-mt} produced numerous models designed for one-to-one translations. Additionally, multilingual models: mBART-50 \cite{liu-2020-mbart}, NLLB-200 \cite{nllb200-2020}, and M2M-100 \cite{fan-2020-m2m100} have also been published, growing popularity as multilingualism has been shown to allow for sharing information among languages \cite{garcia-2020-multilingual}. Most of these models are trained on a diverse set of languages, allowing for many-to-many translation, which is able to translate between any of the supported pairs of languages. This allows the models to generalise over shared lexical and linguistic among languages, and have been shown to increase performance compared to one-to-one translation models \cite{liu-2020-mbart}.

@@

Nevertheless, there does not seem to be much work on comparing or benchmarking different MT-PTMs in machine translation. Intento recently published 'The State of Machine Translation 2024' \cite{intento-2024} providing an in-depth evaluation of 52 MT engines and LLMs across 11 language pairs. Figure \ref{fig:intento_quality} shows the reported translation quality across different domains and language pairs, showing that the results significantly vary based on these parameters. They also reported a lack of growth in the number of supported languages and concluded that translation quality significantly varies depending on languages \cite{intento-2024}. However, the biggest drawback in this report is that the selected LLMs are general LLMs such as GPT-4 \cite{openai-2024-gpt4}, LLaMa2 \cite{touvron-2023-llama2}, and Mistral \cite{jiang-2023-mistral-7b}, instead of MT-specific models.

@@

Corpora simply means a collection of texts, which in this case are used for the purpose of training models. Thus, parallel corpora are defined as sets of texts in a given source language along with their translations in another target language \cite{lefer-2020-parallel-corpora}. They can be bilingual or multilingual and this is crucial for training and evaluating machine translation. Languages without or with limited parallel corpora are referred to as low-resource languages.

Particularly for these low-resource languages, where there are not enough parallel corpora, English has often been used as an intermediary or 'pivot' language. This means texts originally written in languages are first translated into English, and then from English into other languages, resulting in most target texts being translations of translations \cite{lefer-2020-parallel-corpora}. This is called indirect translation and poses many problems in translations as terms can be ambiguous with varying or similar meanings \cite{rosa-2017-indirect-translation-problems}.

Since Neural Machine Translation (NMT) systems require vast amounts of training data, the availability of parallel corpora is crucial for building effective models \cite{koehn-2017-challenges}. The lack of extensive parallel corpora leads to suboptimal performance in NMT techniques \cite{ranathunga-2023-nmt-low-res}. Today, numerous websites, repositories, and datasets exist containing large amounts of parallel texts between specific languages.

OPUS \cite{tiedemann-2012-opus-parallel} provides a comprehensive collection of open-source parallel corpora dedicated to machine translation (MT) tasks. It includes corpora for 744 languages and contains over 1,210 different datasets, amassing a total of 45,945,946,108 sentence pairs. Tatoeba \cite{tatoeba} is another prominent resource in the field of MT and NLP, known for its extensive collection of translated sentences. As of July 2024, it contains 12,186,207 sentences over 423 supported languages, growing daily through volunteer contributions. There are currently
86,915 members contributed through the Tatoeba website.

A number of renowned datasets are commonly used for evaluation in machine translation. The Tatoeba Challenge \cite{tiedemann-2020-tatoeba-challenge} covers 487 languages in 4,024 language pairs, including 657 test sets sourced from the Tatoeba website, covering 138 languages. The TED Talks dataset \cite{ye-2018-word-embeddings-ted} contains transcripts from TED talks for more than 50 languages. IWSLT \cite{agarwal-iwstl-2023} also contains TED talks data, but paired with English translations. Finally, WMT (Conference on Machine Translation) \cite{barrault-2020-wmt}, previously named Workshop on Statistical Machine Translation, is an annual event that organises tasks for machine translation and provides a collection of datasets for benchmarking and evaluating translation systems.

While these datasets can be used to evaluate translation performance between any language pairs, they mostly do not contain parallel corpora across different languages. A corpus between English and French, for example, contains different sets of text than a corpus between English and Spanish. Therefore, they do not support easy evaluation for many-to-English translations. Furthermore, research papers often use different datasets and versions to evaluate their model performance, making direct comparisons even more challenging. mBART \cite{liu-2020-mbart} uses WMT19 for English-German translation and TED15 for Chinese-English translation. M2M-100 \cite{fan-2020-m2m100} uses seven different datasets shared across languages. NLLB-200  \cite{nllb200-2020} uses the FLORES dataset, designed for low-resources languages. OPUS-MT \cite{tiedemann-2023-democratizing,tiedemann-2020-opus-mt} models are evaluated using the datasets from Tatoeba challenges.

@@

@@

Bilingual Evaluation Understudy (BLEU) \cite{papieni-2002-bleu} is the most commonly used metric for machine translation (MT). It assesses how well a candidate translation matches the reference translation by using precision metrics for n-grams and a brevity penalty to ensure a good match in regard to length, word choice, and word order.

@@

The machine translation community relies heavily upon the BLEU score, despite its several drawbacks \cite{lommel-2016-blues}. The metric has been reported to not correlate strongly with human judgement, showing variations in translation that could mean that a higher BLEU score does not necessarily indicate a true enhancement in translation quality \cite{callison-burch-2006-reevaluating-bleu}. Furthermore, the metric is tokenisation-dependant, making it challenging to directly compare BLEU scores between paper \cite{post-2018-sacrebleu}. Thus, the author proposed a standardised variant called SacreBLEU \cite{post-2018-sacrebleu}, which is essentially a Python script that applies its own metric-internal preprocessing and produces the same values as WMT \cite{barrault-2020-wmt}, utilising the WMT (2008–2018) and IWSLT 2017 \cite{cettolo-etal-2017-iwslt} test sets.

@@

Metric for Evaluation of Translation with Explicit ORdering (METEOR) \cite{lavie-2007-meteor} assesses a translation by calculating a score that reflects explicit word-to-word matches between the reference and a candidate translation \cite{agarwal-2008-meteor-mbleu-mter}. It is designed to address some limitations of the BLEU score, allowing matches between simple morphological variants and synonyms. The formula is defined as:
\begin{equation}
    \text{METEOR} = (1 - \gamma \cdot \text{frag}) \cdot \frac{P \cdot R}{\alpha \cdot P + (1 - \alpha) \cdot R}
\end{equation}
where \(P\) is the precision, \(R\) is the recall, and \(\text{frag}\) is the fragmentation penalty. \(\gamma\) is a parameter that controls the weight of the fragmentation penalty, commonly set to 0.5, and \(\alpha\) is a parameter that controls the balance between precision and recall, commonly set to 0.9.

Although the latest official version of METEOR (METEOR-1.5) was released in 2014 \cite{denkowski-lavie-2014-meteor-universal}, the NLTK library \cite{bird-2009-natural} still implements the older version based on the 2007 paper by Lavie and Agarwal \cite{lavie-2007-meteor}. Therefore, this study will use the older version of METEOR, as the calculations will rely on the NLTK library.

@@

OPUS-MT models are taken from the Helsinki-NLP repository through the Hugging Face website \cite{huggingface,zhang-2023-fine-tuning} with the exception of Hebrew-to-English models taken directly from 'tiedeman/opus-mt-he-en'. The 'mbart-large-50-many-to-many-mmt', the 'm2m100\_418M', and the 'nllb-200-distilled-600M' model variants are used for mBART-50 \cite{liu-2020-mbart}, M2M-100 \cite{fan-2020-m2m100}, and NLLB-200 \cite{nllb200-2020}, respectively. Similarly, all multilingual models are downloaded using the transformers \cite{wolf-2020-transformers} library from Hugging Face \cite{huggingface}. A batch size of 4 is used in all models. Translations from each source language to English are first generated through inference and saved into CSV files, before calculating the metrics score.

@@

Table \ref{table:opus_result}, \ref{table:mbart_result}, \ref{table:m2m_result}, and \ref{table:nllb_result}, and  shows the result from all four PTMs. All models perform similarly low on BLEU score (below 10) across all languages, with NLLB-200 reaching 0.01 below on Japanese translation. As BLEU is notoriously unreliable for very short texts, these results are not surprising. The BLEU score can be disproportionately affected by small differences in shorter texts due to the limited number of n-grams available for comparison, as well as the brevity penalty \cite{chatgpt-2024-bleu,papieni-2002-bleu}.

@@

The BLEU, SacreBLEU, and METEOR scores gained by each model, categorised by every language pair are illustrated in Figure \ref{fig:result_visual}. Dutch, Italian, and Ukrainian translations generally score higher across all metrics, suggesting that these languages are well-supported by the pre-trained models. Japanese translations, however, pose significant challenges for all models, as indicated by the consistently low scores across all metrics. Japanese-to-English translation seems to have the worst score on average across the four models, but particularly bad on multilingual models. In contrast, Dutch and German have consistently high results on all models except for NLLB-200, often reaching close to the highest language SacreBLEU and METEOR scores.

@@

Visualisations of the average SacreBLEU and METEOR, categorised by the model (left figures) and language (right figures) are shown in Figure \ref{fig:average_bars}, providing a closer insight into how each model and language perform independently. It can be seen that when averaged across all languages, mBART-50 performs more closely to OPUS-MT on the METEOR score than the SacreBLEU score. Language-wise, Italian, Polish, and Turkish achieve the best average SacreBLEU scores while Chinese, Polish, and Turkish are the top three languages with the highest average METEOR scores.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.9\linewidth]{figures/opus_bleu_comparison.png}
    \caption{Comparison between reported OPUS-MT models performance and performance in this experiment.}
    \label{fig:opus_comparison}
\end{figure}

@@

While this study's experiments resulted in a moderately higher overall SacreBLEU, the dataset used here is also significantly smaller than the full Tatoeba challenge dataset \cite{tiedemann-2020-tatoeba-challenge} that is used in the OPUS-MT reported BLEU. In contrast, this study employs the same set of parallel sentences for all languages, which should lead to more consistent results. Nevertheless, a direct comparison between these results is not fully pertinent.

@@

Additionally, Table \ref{table:opus_comparison} shows the full scores of both results SacreBLEU and reported BLEU from each OPUS-MT model \cite{tiedemann-2020-opus-mt}. The reported BLEU scores are taken from each model card in the HuggingFace repository \cite{huggingface}. Unfortunately, other models are either not benchmarked on the Tatoeba dataset, not evaluated on the source languages used in this study, or use different metrics \cite{liu-2020-mbart,fan-2020-m2m100,nllb200-2020}, and therefore cannot be directly compared to the results of this study.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=1\linewidth]{figures/inference_timings.png}
    \caption{Inference timings for every model.}
    \label{fig:inference_timings}
\end{figure}

@@

This study created a simple dataset containing 1,323 parallel sentence pairs in 14 moderate-to-high-resource languages and evaluated several monolingual and multilingual Machine Translation Pre-Trained Models (MT-PTMs). The findings suggest that while multilingual models have been shown to outperform one-to-one translation models \cite{liu-2020-mbart}, this premise does not necessarily hold in our experiments. Specifically, with a small dataset consisting of short sentences, many-to-English translations across 14 languages with monolingual MT-PTMs (OPUS-MT) outperform unfine-tuned multilingual MT-PTMs (mBART-50, M2M-100, NLLB-200).

OPUS-MT achieves the best performance across all 14 languages. mBART-50 is the second-best-performing model, beating OPUS-MT only in Polish SacreBLEU. Nevertheless, both the mBART-50 and the M2M-100 models perform generally well in all languages. NLLB-200, however, achieves much lower scores in both SacreBLEU and METEOR for all languages except for Chinese, slightly outperforming M2M-100 but still slightly below mBART-50. NLLB-200 should then be avoided for use without any further fine-tuning on these languages. Note that the distilled version is used in this study for NLLB-200 instead of the larger 3.3 billion parameters model variant.

@@

In curating the dataset, only the first translation of the same English phrases was taken, while additional translations were discarded. This ignores several possible translation references which might include synonyms or different phrasings, thus potentially affecting the evaluation score, especially for BLEU and SacreBLEU metrics. Moreover, the dataset mainly consists of short sentences with limited linguistic depth. Whether the result of this study would stay consistent with longer sentences or more complex documents should be further explored. The Tatoeba dataset \cite{tiedemann-2020-tatoeba-challenge} consisting of short sentences has been reported to be too optimistic when evaluated with other datasets that are more realistic \cite{tiedemann-2020-opus-mt}.

The METEOR implementation in this study through the NLTK library is based on the original METEOR paper \cite{lavie-2007-meteor}, which is described as "relatively simple and naive." A newer version, METEOR-1.5 \cite{denkowski-lavie-2014-meteor-universal} offers improved features and has been reported to produce significantly different results \cite{tuetschek-2021-meteor-issue-nltk}. Therefore, reevaluating translation models using the updated metric could be beneficial.
